\documentclass{article}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[
	tmargin=0.8in,
	bmargin=0.5in,
	lmargin=0.75in,
	rmargin=0.75in
]{geometry}
\newfontfamily\namefont{Calibri}[
	Letters=SmallCaps,
]
% section
\newfontfamily\sectionfont{Calibri}[]
\setmainfont{Calibri}
\titleformat{\section}[hang]{\filcenter\fontsize{12}{15}\bfseries\sectionfont\uppercase}{}{0pt}{
	\vspace{-4pt}
	\rule{\textwidth}{1pt}
}[
	\vspace{-10.5pt}
	\rule{\textwidth}{1pt}
]
\titlespacing*{\section}{0pt}{-18pt}{-5pt}[0pt]
% subsection
\newfontfamily\subsectionfont{Calibri}[]
\titleformat{\subsection}[hang]{\fontsize{10.5}{13}\subsectionfont}{}{0pt}{}[]
\titlespacing*{\subsection}{-2pt}{0pt}{0pt}[0pt]
% paragraph
\newfontfamily\paragraphfont{Calibri}[]
\titleformat{\paragraph}[hang]{\fontsize{10.5}{13}\paragraphfont\itshape\bfseries}{}{0pt}{}[]
\titlespacing*{\paragraph}{0pt}{0pt}{0pt}[0pt]
% lists
\setlist{nolistsep}
\begin{document}
	\begin{center}
		{\namefont \fontsize{18}{24}\selectfont \textbf{Stephen Krider}}

		\vspace{0.075in}
		
		(818) 424-3623
		\char"00B7 
		\char"0020
		skrider@berkeley.edu 
		\char"00B7 
		\char"0020
		linkedin.com/in/skrider
	\end{center}
	\vspace{-17pt}
	\section{Education \& Coursework}
	\subsection{
		{\bfseries UC Berkeley - Management, Entrepreneurship, \& Technology Program}
		{\hspace{\fill}\bfseries Expected June 2024}
	}
	Dual Degree: B.S. EECS/B.S. Business Administration

	\noindent 3.5 GPA

	\noindent Related Coursework: EECS 189 (Machine Learning), CS 170 (Algorithms), EECS 127 (Convex Optimization), EECS 16B (Circuit Design and Controls), CS 61C (Computer Architecture) 
	
	\section{Related Experience}

	\subsection{
		\textbf{Zeal}, San Francisco, CA 
		{\hspace{\fill}\bfseries Jun. 2021 - Dec. 2021}
	}
	{\itshape Series-A fintech startup providing an API for integrating payroll processing into SaaS products.}
	\paragraph{Software Engineer Intern}
	\begin{itemize}
		\item Developed a full-stack web application, Kday, geared towards processing payroll for family businesses, as a demonstration of Zeal’s product, using React, Redux, Express, MongoDB, TypeScript
		\item Lead design, planning, and development of Kday, following best engineering practices
	\end{itemize}
	\paragraph{Software Engineer}
	\begin{itemize}
		\item Built React component library in Typescript
		\item Built PDF manipulation software in Node.js for filling out a wide range of state and federal tax forms
	\end{itemize}

	\vspace{14pt}

	\subsection{
		\textbf{Yeti Finance}, San Francisco, CA 
		{\hspace{\fill}\bfseries Dec. 2021 - Jan. 2022}
	}
	{\itshape Seed-funded decentralized Finance startup that manages a lending protocol on the Avalanche network enabling customers to borrow against their portfolio of blockchain assets and cryptocurrencies.}
	\paragraph{Software Contractor}
	\begin{itemize}
		\item Architected and built frontend for Yeti using React, Typescript, Storybook, and Chakra-ui
	\end{itemize}

	\vspace{14pt}

	\subsection{
		\textbf{Zocdoc}, New York, NY 
		{\hspace{\fill}\bfseries Jun. 2022 - Aug. 2022}
	}
	{\itshape Zocdoc is a SaaS tech company that connects patients to medical care providers.}
	\paragraph{Software Engineer Intern}
	\begin{itemize}
		\item Built internal tool with AWS and C# to securely store long-term patient data
		\item Streamlined audit processes
	\end{itemize}
\end{document}

